---
title: 'Basic R Syntax and Data Types'

execute: 
  include: false
---

# Instructions

The purpose of this exercise is to practice and reinforce your understanding of basic R syntax and data types. In this exercise, you will be working with variables, vectors, matrices, and data frames.

# Tasks

1.  Create a variable called "player_name" and assign it the name of your favorite sports player as a character.

    ```{r}

    player_name <- "Muhammad Ali"

    player_name
    ```

2.  Create a variable called "player_age" and assign it the age of your favorite sports player as a numeric value.

    ```{r}

    player_age <- 81 #If he were alive today

    player_age
    ```

3.  Create a variable called "is_active" and assign it a logical value of TRUE if your favorite sports player is still playing, and FALSE if they are no longer playing.

    ```{r}
    is_active <- FALSE

    is_active
    ```

4.  Create a vector called "goats" with the names of your 5 favorite athletes.

    ```{r}
    goats <- c('Muhammad Ali', 
               'Mahmoud Abdul-Rauf', 
               'Colin Kaepernick',
               'Jackie Robinson',
               'Arthur Ashe')

    goats
    ```

5.  Access the youngest athlete from the goats vector.

    ```{r}

    goats[3]
    ```

6.  Create a matrix called "player_data" with two columns: "name" and "sport". Fill in the matrix with the name and sports of your favorite athletes.

    ```{r}

    player_data <- data.frame(players = c('Muhammad Ali', 
                                          'Mahmoud Abdul-Rauf',
                                          'Colin Kaepernick',
                                          'Jackie Robinson',
                                          'Arthur Ashe'),
                              sports  = c('Boxing', 
                                          'Basketball',
                                          'Football',
                                          'Baseball',
                                          'Tennis'))


    player_data


    # You can also create the data.frame by also referencing the goats vector created earlier.
    player_data2 <- data.frame(players = goats,
                              sports  = c('Boxing', 
                                          'Basketball',
                                          'Football',
                                          'Baseball',
                                          'Tennis'))

    player_data2
    ```

7.  Access the players column of the player_data data frame.

    ```{r}

    # The players column can be accessed by index
    player_data[1]
    ```

8.  Retrieve a vector of all of the sports in sports column of the player_data data frame.

    ```{r}
    player_data$sports
    ```

9.  Print the class of each variable created in the exercises.

    ```{r}
    print(class(player_name))
    print(class(player_age))
    print(class(is_active))
    print(class(player_data))
    ```
