---
title: 'Basic Operations in R'

execute: 
  include: true
---

# Instructions

In this assignment, you will apply your knowledge of basic operations and functions in R to solve various problems. Follow the instructions for each task and write your code accordingly. Make sure to run your code and verify that it produces the expected output.

# Background Informations

Team

| Player  | Position | Points | Assists | Rebounds | Blocks |
|---------|----------|--------|---------|----------|--------|
| Newton  | Center   | 20     | 5       | 13       | 5      |
| Seale   | Forward  | 15     | 4       | 8        | 2      |
| Davis   | Forward  | 16     | 5       | 9        | 0      |
| Hampton | Guard    | 32     | 7       | 5        | 1      |
| Clark   | Guard    | 15     | 12      | 2        | 0      |

: Oakland Panthers Strating Lineup Stats

# Tasks

1.  Arithmetic Operations - Calculate the following:

    -   59 plus 83

    -   112 minus 37

    -   16 times 13

    -   2048 divided by 32

    -   8 cubed (or 8 to the 3rd power)

    ```{r}

    59 + 83
    112 - 37
    16 * 13
    2048 / 32
    8 ^ 3
    ```

2.  Assignment Operator - Make the same calculations and assign them to their respective variables:

    -   add_num for the addition answer

    -   sub_num for the subtraction answer

    -   mult_num for the multiplication answer

    -   div_num for the division answer

    -   exp_num for the exponential answer

    ```{r}

    add_num  <- 59 + 83
    sub_num  <- 112 - 37
    mult_num <- 16 * 13
    div_num  <- 2048 / 32
    exp_num  <- 8 ^ 3
    ```

3.  Comparison Operators - Make the following comparisons:

    -   Is add_num equal to 208?

    -   Is add_num not equal to 208?

    -   Is sub_num greater than add_num?

    -   Is mult_num less than 208?

    -   Is mult_num greater than or equal to 208?

    -   Is exp_num less than or equal to 208?

    ```{r}
    add_num  == 208
    add_num  != 208 
    sub_num  >  add_num
    mult_num < 208
    mult_num >= 208
    exp_num  <= 208
    ```

4.  Logical Operators - Use logical operators to make the following comparisons:

    -   Are both 100 and 200 greater than add_num?

    -   Is 100 or 200 greater than add_num?

    ```{r}

    100 > add_num & 200 > add_num
    100 < add_num | 200 < add_num
    ```

5.  Built-in Functions:

    -   **`print()`**: Displays the output on the console.

    -   **`sum()`**: Calculates the sum of values.

    -   **`mean()`**: Calculates the mean of values.

    -   **`length()`**: Returns the length of an object.

    -   **`max()`**: Returns the maximum value in a vector.

    -   **`min()`**: Returns the minimum value in a vector.

    -   **`sqrt()`**: Calculates the square root of a value.

    -   **`round()`**: Rounds a number to the nearest integer.
